---
title: "Melbourne House Pricing"
author: "Paolo Coraggio"
date: "31/01/2020"
output: 
    ioslides_presentation:
        transition: slower
---

```{r setup, include=FALSE}
library(plotly)
library(dplyr)
library(ggplot2)


knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- [Kaggle](https://www.kaggle.com/) is an online community of data scientists and machine learning practitioners that contains different datasets that can be used for training and testing algorithms for Data Analysis
- `melb_data.csv` is a free available database, from Kaggle, containing information about Melbourne, Australia houses market 
- The goal of this project is to plot, on the city map, some information about 1000 sampled data from the dataset 
- The map can be used as basis for futher analysis

## Dataset Information

- The dataset size is:
```{r, echo = FALSE}
df.mel <- read.csv("./Data/melb_data.csv")
```

```{r}
dim(df.mel)
```

- And contains the following information
```{r}
names(df.mel)
```

## Dataset Transformation

- The dataset has been reduced by deleting all rows that do not contain information about the house longitude and latitude 
- A further variable has been also added to split the dataset in 4 different prices categories:
    - Low Price (up to 640000\$)
    
    - Medium Low Price (from 640000\$ to  900000\$)
    - Medium High Price (from 900000\$ to 1320000\$)
    - High Price (from 1320000\$ to 9000000\$)

- A sample of 1000 houses has been extracted from the original database in order to plot the information on the map

## House Pricing Map

```{r, echo = FALSE, warning=FALSE, message=FALSE}
df.mel <- df.mel[!(is.na(df.mel$Longtitude)),]
df.mel$PriceCategory <-cut(df.mel$Price,
                       breaks = quantile(df.mel$Price),
                       labels = c("low", "medium low", "medium high", "high"))

df.mel$MarkerColor <-cut(df.mel$Price,
                     breaks = quantile(df.mel$Price),
                     labels = c("green", "lightgreen", "orange", "red"))

n.sample <- 1000
df.melsampled <- df.mel[sample(nrow(df.mel), n.sample),]

df.melsampled$HoverText <- with(df.melsampled, 
                                paste('<b>Price:</b>', Price,
                                      '<br>', "Council: ", CouncilArea, 
                                      '<br>', "Region: ", Regionname, 
                                      '<br>', "Number of Rooms", Rooms))


plot_ly(df.melsampled, type = "scattermapbox") %>%
    add_trace(lat = filter(df.melsampled, PriceCategory == "low")$Lattitude,
              lon = filter(df.melsampled, PriceCategory == "low")$Longtitude,
              color = "Low Price",
              marker = list(color = "darkgreen"),
              hoverinfo = "text",
              hovertext = filter(df.melsampled, PriceCategory == "low")$HoverText,
              mode = "markers")%>%
    add_trace(lat = filter(df.melsampled, PriceCategory == "medium low")$Lattitude,
              lon = filter(df.melsampled, PriceCategory == "medium low")$Longtitude,
              color = "Medium Low Price",
              marker = list(color = "green"),
              hoverinfo = "text",
              hovertext = filter(df.melsampled, PriceCategory == "medium low")$HoverText,
              mode = "markers") %>%
    add_trace(lat = filter(df.melsampled, PriceCategory == "medium high")$Lattitude,
              lon = filter(df.melsampled, PriceCategory == "medium high")$Longtitude,
              color = "Medium High Price",
              marker = list(color = "orange"),
              hovertext = filter(df.melsampled, PriceCategory == "medium high")$HoverText,
              hoverinfo = "text",
              mode = "markers")%>%
    add_trace(lat = filter(df.melsampled, PriceCategory == "high")$Lattitude,
              lon = filter(df.melsampled, PriceCategory == "high")$Longtitude,
              color = "High Price",
              marker = list(color = "red"),
              hovertext = filter(df.melsampled, PriceCategory == "high")$HoverText,
              hoverinfo = "text",
              mode = "markers")%>%
    layout(
        mapbox = list(
            style = 'open-street-map',
            zoom =9.5,
            center = list(lon = mean(df.melsampled$Longtitude), 
                          lat = mean(df.melsampled$Lattitude)))
    ) 
```

## Acknowledgment

- Map generated using `Plotly` library and `OpenStreetMap`.

- The dataset is from [Kaggle](https://www.kaggle.com/) organisation.
All code, data and further information are available on GitHub:

    +  [https://github.com/pacoraggio/DevelopingDataProductWeek3](https://github.com/pacoraggio/DevelopingDataProductWeek3)

- Please feel free to contact me if you have any suggestion/correction.
