---
title: "Melbourne House Pricing"
author: "Paolo Coraggio"
date: "31/01/2020"
output: html_document
---

```{r setup, include=FALSE}
library(plotly)
library(dplyr)
library(ggplot2)

knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This webpage shows information about House Pricing in Melbourne from 1000 houses randomly sampled from the Melboune House Pricing database from [Intro to Machine Learning](https://www.kaggle.com/learn/intro-to-machine-learning) Kaggle course. The map shows the location of the house and basic information about its price. The house prices are divided in four categories:

- Low Price
- Medium Low Price
- Medium High Price
- High Price

For each house information about the price, location district and county and number of rooms are displayed

## Melbourne House Pricing Map

```{r, echo=FALSE, warning=FALSE, message=FALSE}
df.mel <- read.csv("./Data/melb_data.csv")
df.mel <- df.mel[!(is.na(df.mel$Longtitude)),]
df.mel$PriceCategory <-cut(df.mel$Price,
                       breaks = quantile(df.mel$Price),
                       labels = c("low", "medium low", "medium high", "high"))

df.mel$MarkerColor <-cut(df.mel$Price,
                     breaks = quantile(df.mel$Price),
                     labels = c("green", "lightgreen", "orange", "red"))
```

Now let's plot the data on a map a sampled number of houses

```{r, fig.width=9.5, echo= FALSE, warning=FALSE, message=FALSE}
n.sample <- 1000
df.melsampled <- df.mel[sample(nrow(df.mel), n.sample),]

df.melsampled$HoverText <- with(df.melsampled, 
                                paste('<b>Price:</b>', Price,
                                      '<br>', "Council: ", CouncilArea, 
                                      '<br>', "Region: ", Regionname, 
                                      '<br>', "Number of Rooms", Rooms))


plot_ly(df.melsampled, type = "scattermapbox") %>%
    add_trace(lat = filter(df.melsampled, PriceCategory == "low")$Lattitude,
              lon = filter(df.melsampled, PriceCategory == "low")$Longtitude,
              color = "Low Price",
              marker = list(color = "darkgreen"),
              hoverinfo = "text",
              hovertext = filter(df.melsampled, PriceCategory == "low")$HoverText,
              mode = "markers")%>%
    add_trace(lat = filter(df.melsampled, PriceCategory == "medium low")$Lattitude,
              lon = filter(df.melsampled, PriceCategory == "medium low")$Longtitude,
              color = "Medium Low Price",
              marker = list(color = "green"),
              hoverinfo = "text",
              hovertext = filter(df.melsampled, PriceCategory == "medium low")$HoverText,
              mode = "markers") %>%
    add_trace(lat = filter(df.melsampled, PriceCategory == "medium high")$Lattitude,
              lon = filter(df.melsampled, PriceCategory == "medium high")$Longtitude,
              color = "Medium High Price",
              marker = list(color = "orange"),
              hovertext = filter(df.melsampled, PriceCategory == "medium high")$HoverText,
              hoverinfo = "text",
              mode = "markers")%>%
    add_trace(lat = filter(df.melsampled, PriceCategory == "high")$Lattitude,
              lon = filter(df.melsampled, PriceCategory == "high")$Longtitude,
              color = "High Price",
              marker = list(color = "red"),
              hovertext = filter(df.melsampled, PriceCategory == "high")$HoverText,
              hoverinfo = "text",
              mode = "markers")%>%
    layout(
        mapbox = list(
            style = 'open-street-map',
            zoom =9.5,
            center = list(lon = mean(df.melsampled$Longtitude), 
                          lat = mean(df.melsampled$Lattitude)))
    ) 
    
```

## Acknowledgment and details info

The dataset is from [Kaggle](https://www.kaggle.com/) organisation.
All code, data and further information are available on GitHub:

[https://github.com/pacoraggio/DevelopingDataProductWeek3](https://github.com/pacoraggio/DevelopingDataProductWeek3)

Please feel free to contact me if you have any suggestion/correction.
